DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-08 Draft-Ped-Metrics-Example.Rmd
names cached chunk

```{r, cache = TRUE}
library(tidyverse)
library(sf)

@@

```{r}
score_interpretation <- tribble(
  ~score_at_least, ~interpretation,
  10, "Good",
  5, "Adequate",
  3, "Minimum",
  1, "Poor",
  0, "Nothing"
)

>>>>

```{r kitsapmap, cache = TRUE}
library(tidyverse)
library(sf)

@@

```{r}
score_interpretation <- tribble(
  ~score_at_least, ~interpretation,
  10, "Good",
  5, "Adequate",
  3, "Minimum",
  1, "Poor",
  0.001, "Very Poor",
  0, "Nothing"
)
